---
title: "speed"
author: "Alessandro Ciancetta"
date: "18/3/2021"
output: html_document
---

aosifabgbfnpa

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Monte Carlo simulation

Example of a simple Monte Carlo computation of the area of a unit circle following <https://www.youtube.com/watch?v=EaR3C4e600k>.

Consider a **unit circle**. We can build a $2 \times 2$ square to envelope it. The Area of the circle is $\pi/4$. This can be approximated by sampling many points in the square and by computing the fraction of those points also laying within the circle.

```{r cars}
sampler <- function(N){
  circle <- 0 
for(i in 1:N){
 # cat(paste0(round((i/N)*100,2), "%"), " \r")
  x <- runif(1, min = -1, max = 1)
  y <- runif(1, min = -1, max = 1)
  if(x^2 + y^2 <= 1){
    circle <- circle + 1
  }
}
results <- c(estimate = circle/N, true =  pi/4)
abs(diff(results))
}

sampler(10^5)
```

We could improve the code as follows:

```{r}
sampler_A <- function(N){
  circle <- 0 
  for(i in 1:N){
   # cat(paste0(round((i/N)*100,2), "%"), " \r")
    x <- runif(1, min = -1, max = 1)
    y <- runif(1, min = -1, max = 1)
    circle <- circle + (x^2 + y^2 <= 1)*1
  }
results <- c(estimate = circle/N, true =  pi/4)
abs(diff(results))
}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
